---
title: "SARS-CoV-2 Antibody Analysis"
author: "Macauley Locke"
date: "09/06/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Introduction

The following document has been generated to provide methodology used to obtain statistics shown within the paper "Pre-existing humoral immunity to common human coronaviruses negatively impacts the protective SARS-CoV-2 antibody response" summarizing antibody responses during SARS-COV-2 infections and vaccination. The following analysis has been undertaken by Macauley Locke (University of Leeds) and Chun-Yang Lin (St Jude children hospital) supervised by Charles Taylor (University of Leeds), Maureen Mcgargill (St Jude Children hospital) and Carmen Molina Paris (University of Leeds & Los Alasmos National Laboratory). This longitudinal study examines staff at the hospital taking into account not only those who have been infected with SARS-COV-2 but also vaccine responses. Please also see file "Severity_Kendall.r" for analysis of correlations between severity and antibody response.


## Package load

Personal standard packages to be loaded. Not all packages will be called on within this script.

```{r,warning=FALSE}
library(car);
library(excel.link);
library(ggfortify);
#library(pca3d);
library(factoextra);
library("FactoMineR");
library(corrplot);
library(Hmisc);
library(plotly);
library(MVN);
library(psych);
library(tidyr);
library(tidyverse);
library(energy);
library(ggplot2);
library(ggjoy);
library(dplyr);
library(data.table);
library(viridis);
library("PerformanceAnalytics");
library(TestCor)
library(readxl)
```

Set working directory

```{r}
setwd("/Users/macau/Documents/St Jude HLA Data/Antibody Data")
```

Read in data for Antibody study complete

```{r}
Antibody_Data<-as.data.frame(read_excel("Complete_antibody_data_St_Jude28072021 Corrected.xlsx"))

```
Read data for Pfizer vaccine data only. This is due to samples for this vaccine being significantly larger than other vaccines presented within this study. Pfizer=261.

```{r}
Vaccine_Data<-as.data.frame(read_excel("Complete_antibody_data_St_Jude28072021 Corrected.xlsx",sheet = "Only Pfizer with CCOV"))
```


Remove first column with update for antibody dataframe
```{r}
Antibody_Data<-subset(Antibody_Data, select = -c(1) )
```

Remove first column with update for Vaccine dataframe
```{r}
Vaccine_Data<-subset(Vaccine_Data, select = -c(1) )
```


Identify column index for use in work.
```{r}

col_list=c(which(colnames(Antibody_Data)=="SJTRCID"),
           which(colnames(Antibody_Data)=="Sample type"),
           which(colnames(Antibody_Data)=="Days post Last Vax"),
           which(colnames(Antibody_Data)=="RBD_IgG"),
           which(colnames(Antibody_Data)=="Spike_IgG"),
           which(colnames(Antibody_Data)=="N_IgG"),
           which(colnames(Antibody_Data)=="RBD_IgM"),
           which(colnames(Antibody_Data)=="Spike_IgM"),
           which(colnames(Antibody_Data)=="N_IgM"),
           which(colnames(Antibody_Data)=="RBD_IgA"),
           which(colnames(Antibody_Data)=="Spike_IgA"),
           which(colnames(Antibody_Data)=="N_IgA"),
           which(colnames(Antibody_Data)=="OC43_IgG"),
           which(colnames(Antibody_Data)=="NL63_IgG"),
           which(colnames(Antibody_Data)=="229E_IgG"),
           which(colnames(Antibody_Data)=="HKU1_IgG"),
           which(colnames(Antibody_Data)=="OC43_IgM"),
           which(colnames(Antibody_Data)=="NL63_IgM"),
           which(colnames(Antibody_Data)=="229E_IgM"),
           which(colnames(Antibody_Data)=="HKU1_IgM"),
           which(colnames(Antibody_Data)=="OC43_IgA"),
           which(colnames(Antibody_Data)=="NL63_IgA"),
           which(colnames(Antibody_Data)=="229E_IgA"),
           which(colnames(Antibody_Data)=="HKU1_IgA"))
```

# Question 1 
## Correlations between CCOV at Baseline and Acute and Convalescent samples taken from 16-40 days post symptom onset


Extract individuals who have not received a vaccine based on last vaccine day column, and who have symptom onset reported between 16-40 days
```{r}

#Extract all Baseline readings
Baseline<-Antibody_Data[Antibody_Data$`Sample type`=="Baseline",col_list]

#Extract Acute and Convalescent Samples with Symptom onset between 16-40 Days
Acute_temp<-Antibody_Data[Antibody_Data$`Sample type`=="Acute" & Antibody_Data$`Days post First Symptom onset`>15 & Antibody_Data$`Days post First Symptom onset`<41 & Antibody_Data$`Days post Last vax`<0,col_list]
Convalescent_temp<-Antibody_Data[Antibody_Data$`Sample type`=="Convalescent" & Antibody_Data$`Days post First Symptom onset`>15 & Antibody_Data$`Days post First Symptom onset`<41 & Antibody_Data$`Days post Last vax`<0,col_list]

Acute_temp<-Acute_temp[complete.cases(Acute_temp),]
Convalescent_temp<-Convalescent_temp[complete.cases(Convalescent_temp),]
Infectives<-rbind(Acute_temp,Convalescent_temp)

Merged<- merge(y=Infectives, x=Baseline, by="SJTRCID", all=TRUE,suffixes = c(".Baseline",".Infectives"));

Finalset<-Merged[complete.cases(Merged),]

```

Pairs panels with linear regression models fitted for RBD & SPike for IgG
```{r}
temp<-Finalset[,c(14,13,12,15,16,18,17,19,20,22,21,23,25,26,27)]
pairs.panels(temp, 
             method = "pearson", # correlation method
             hist.col = "#00AFBB",
             density = TRUE,  # show density plots
             ellipses = FALSE,  # show correlation ellipses
             cor = TRUE,
             stars = TRUE,
             cex.cor = 2,
             lm=TRUE)

ApplyFdrCor(
temp,
alpha = 0.05,
stat_test = "fisher",
method = "LCTnorm",
Nboot = 1,
vect = FALSE,
arr.ind = FALSE
)
```

Pairs panels with linear regression models fitted for RBD & SPike for IgM
```{r}
temp<-Finalset[,c(14,13,12,15,16,18,17,19,20,22,21,23,28,29,30)]
pairs.panels(temp, 
             method = "pearson", # correlation method
             hist.col = "#00AFBB",
             density = TRUE,  # show density plots
             ellipses = FALSE,  # show correlation ellipses
             cor = TRUE,
             stars = TRUE,
             cex.cor = 3,
             lm=TRUE)


ApplyFdrCor(
temp,
alpha = 0.05,
stat_test = "fisher",
method = "LCTnorm",
Nboot = 1000,
vect = FALSE,
arr.ind = FALSE
)
```

Pairs panels with linear regression models fitted for RBD & SPike for IgA
```{r}
temp<-Finalset[,c(14,13,12,15,16,18,17,19,20,22,21,23,31,32,33)]
pairs.panels(temp, 
             method = "pearson", # correlation method
             hist.col = "#00AFBB",
             density = TRUE,  # show density plots
             ellipses = FALSE,  # show correlation ellipses
             cor = TRUE,
             stars = TRUE,
             cex.cor = 3,
             lm=TRUE)

ApplyFdrCor(
temp,
alpha = 0.05,
stat_test = "fisher",
method = "LCTnorm",
Nboot = 1000,
vect = FALSE,
arr.ind = FALSE
)

```

# Question 2 
## Correlations between CCOV at Baseline percentge boost and Acute and Convalescent samples taken from 16-40 days post symptom onset


Extract indiviudals who have not recieved a vaccine based on last vaccine day column, and who have results reported between 16-40 days. Calculate boost for each patient.
```{r}

#Extract all Baseline readings
Baseline<-Antibody_Data[Antibody_Data$`Sample type`=="Baseline",col_list]

#Extract Acute and Convalescent Samples with Symptom onset between 16-40 Days
Acute_temp<-Antibody_Data[Antibody_Data$`Sample type`=="Acute" & Antibody_Data$`Days post First Symptom onset`>15 & Antibody_Data$`Days post First Symptom onset`<41& Antibody_Data$`Days post Last vax`<0,col_list]
Convalescent_temp<-Antibody_Data[Antibody_Data$`Sample type`=="Convalescent" & Antibody_Data$`Days post First Symptom onset`>15 & Antibody_Data$`Days post First Symptom onset`<41 & Antibody_Data$`Days post Last vax`<0,col_list]

Acute_temp<-Acute_temp[complete.cases(Acute_temp),]
Convalescent_temp<-Convalescent_temp[complete.cases(Convalescent_temp),]
Infectives<-rbind(Acute_temp,Convalescent_temp)

Merged<- merge(y=Infectives, x=Baseline, by="SJTRCID", all=TRUE,suffixes = c(".Baseline",".Infectives"));

Finalset<-Merged[complete.cases(Merged),]

#Boost IgG
Finalset$OC34IgGBoost<-(Finalset[,34]-Finalset[,12])/Finalset[,12]
Finalset$NL63IgGBoost<-(Finalset[,35]-Finalset[,13])/Finalset[,13]
Finalset$`229EIgGBoost`<-(Finalset[,36]-Finalset[,14])/Finalset[,14]
Finalset$`HKU1IgGBoost`<-(Finalset[,37]-Finalset[,15])/Finalset[,15]

#Boost IgM
Finalset$`OC43IgMBoost`<-(Finalset[,38]-Finalset[,16])/Finalset[,16]
Finalset$NL63IgMBoost<-(Finalset[,39]-Finalset[,17])/Finalset[,17]
Finalset$`229EIgMBoost`<-(Finalset[,40]-Finalset[,18])/Finalset[,18]
Finalset$`HKU1IgMBoost`<-(Finalset[,41]-Finalset[,19])/Finalset[,19]

#Boost IgA
Finalset$`OC43IgABoost`<-(Finalset[,42]-Finalset[,20])/Finalset[,20]
Finalset$NL63IgABoost<-(Finalset[,43]-Finalset[,21])/Finalset[,21]
Finalset$`229EIgABoost`<-(Finalset[,44]-Finalset[,22])/Finalset[,22]
Finalset$`HKU1IgABoost`<-(Finalset[,45]-Finalset[,23])/Finalset[,23]
```

CCOV Boost from baseline to Acute/Convalescent compared to IgG Acute/Convalescent
```{r}
temp<-Finalset[,c(46,47,48,49,50,51,52,53,54,55,56,57,25,26,27)]

pairs.panels(temp, 
             method = "pearson", # correlation method
             hist.col = "#00AFBB",
             density = TRUE,  # show density plots
             ellipses = FALSE,  # show correlation ellipses
             cor = TRUE,
             stars = TRUE,
             cex.cor = 3,
             lm=TRUE)

ApplyFdrCor(
temp,
alpha = 0.05,
stat_test = "fisher",
method = "LCTnorm",
Nboot = 1000,
vect = FALSE,
arr.ind = FALSE
)
```

CCOV Boost from baseline to Acute/Convalescent compared to IgM Acute/Convalescent
```{r}
temp<-Finalset[,c(46,47,48,49,50,51,52,53,54,55,56,57,28,29,30)]

pairs.panels(temp, 
             method = "pearson", # correlation method
             hist.col = "#00AFBB",
             density = TRUE,  # show density plots
             ellipses = FALSE,  # show correlation ellipses
             cor = TRUE,
             stars = TRUE,
             cex.cor = 3,
             lm=TRUE)
ApplyFdrCor(
temp,
alpha = 0.05,
stat_test = "fisher",
method = "LCTnorm",
Nboot = 1000,
vect = FALSE,
arr.ind = FALSE
)

```

CCOV Boost from baseline to Acute/Convalescent compared to IgA Acute/Convalescent
```{r}
temp<-Finalset[,c(46,47,48,49,50,51,52,53,54,55,56,57,31,32,33)]

pairs.panels(temp, 
             method = "pearson", # correlation method
             hist.col = "#00AFBB",
             density = TRUE,  # show density plots
             ellipses = FALSE,  # show correlation ellipses
             cor = TRUE,
             stars = TRUE,
             cex.cor = 3,
             lm=TRUE)

ApplyFdrCor(
temp,
alpha = 0.05,
stat_test = "fisher",
method = "LCTnorm",
Nboot = 1000,
vect = FALSE,
arr.ind = FALSE
)


```

#Question 3
## Examine boost 1-15 days post sympton onset

Extract indiviudals who have not recieved a vaccine based on last vaccine day column, and who have results reported between 16-40 days
```{r}

#Extract all Baseline readings
Baseline<-Antibody_Data[Antibody_Data$`Sample type`=="Baseline",col_list]

#Extract Acute and Convalescent Samples with Symptom onset between 1-5 Days
Acute_temp<-Antibody_Data[Antibody_Data$`Sample type`=="Acute" & Antibody_Data$`Days post First Symptom onset`>0 & Antibody_Data$`Days post First Symptom onset`<16& Antibody_Data$`Days post Last vax`<0,col_list]
Convalescent_temp<-Antibody_Data[Antibody_Data$`Sample type`=="Convalescent" & Antibody_Data$`Days post First Symptom onset`>0 & Antibody_Data$`Days post First Symptom onset`<16 ,col_list]

Acute_temp<-Acute_temp[complete.cases(Acute_temp),]
Convalescent_temp<-Convalescent_temp[complete.cases(Convalescent_temp),]
Infectives<-rbind(Acute_temp,Convalescent_temp)

Merged<- merge(y=Infectives, x=Baseline, by="SJTRCID", all=TRUE,suffixes = c(".Baseline",".Infectives"));

Finalset<-Merged[complete.cases(Merged),]

#Boost IgG
Finalset$OC34IgGBoost<-(Finalset[,34]-Finalset[,12])/Finalset[,12]
Finalset$NL63IgGBoost<-(Finalset[,35]-Finalset[,13])/Finalset[,13]
Finalset$`229EIgGBoost`<-(Finalset[,36]-Finalset[,14])/Finalset[,14]
Finalset$`HKU1IgGBoost`<-(Finalset[,37]-Finalset[,15])/Finalset[,15]

#Boost IgM
Finalset$`OC43IgMBoost`<-(Finalset[,38]-Finalset[,16])/Finalset[,16]
Finalset$NL63IgMBoost<-(Finalset[,39]-Finalset[,17])/Finalset[,17]
Finalset$`229EIgMBoost`<-(Finalset[,40]-Finalset[,18])/Finalset[,18]
Finalset$`HKU1IgMBoost`<-(Finalset[,41]-Finalset[,19])/Finalset[,19]

#Boost IgA
Finalset$`OC43IgABoost`<-(Finalset[,42]-Finalset[,20])/Finalset[,20]
Finalset$NL63IgABoost<-(Finalset[,43]-Finalset[,21])/Finalset[,21]
Finalset$`229EIgABoost`<-(Finalset[,44]-Finalset[,22])/Finalset[,22]
Finalset$`HKU1IgABoost`<-(Finalset[,45]-Finalset[,23])/Finalset[,23]
```


CCOV Boost from baseline to Acute/Convalescent compared to IgG Acute/Convalescent
```{r}
temp<-Finalset[,c(46,47,48,49,50,51,52,53,54,55,56,57,25,26,27)]

pairs.panels(temp, 
             method = "pearson", # correlation method
             hist.col = "#00AFBB",
             density = TRUE,  # show density plots
             ellipses = FALSE,  # show correlation ellipses
             cor = TRUE,
             stars = TRUE,
             cex.cor = 3,
             lm=TRUE)
ApplyFdrCor(
temp,
alpha = 0.05,
stat_test = "fisher",
method = "LCTnorm",
Nboot = 1000,
vect = FALSE,
arr.ind = FALSE
)


```

CCOV Boost from baseline to Acute/Convalescent compared to IgM Acute/Convalescent
```{r}
temp<-Finalset[,c(46,47,48,49,50,51,52,53,54,55,56,57,28,29,30)]

pairs.panels(temp, 
             method = "pearson", # correlation method
             hist.col = "#00AFBB",
             density = TRUE,  # show density plots
             ellipses = FALSE,  # show correlation ellipses
             cor = TRUE,
             stars = TRUE,
             cex.cor = 3,
             lm=TRUE)

ApplyFdrCor(
temp,
alpha = 0.001,
stat_test = "fisher",
method = "LCTnorm",
Nboot = 1000,
vect = FALSE,
arr.ind = FALSE
)

```


CCOV Boost from baseline to Acute/Convalescent compared to IgA Acute/Convalescent
```{r}
temp<-Finalset[,c(46,47,48,49,50,51,52,53,54,55,56,57,31,32,33)]

pairs.panels(temp, 
             method = "pearson", # correlation method
             hist.col = "#00AFBB",
             density = TRUE,  # show density plots
             ellipses = FALSE,  # show correlation ellipses
             cor = TRUE,
             stars = TRUE,
             cex.cor = 3,
             lm=TRUE)
ApplyFdrCor(
temp,
alpha = 0.0,
stat_test = "fisher",
method = "LCTnorm",
Nboot = 1000,
vect = FALSE,
arr.ind = FALSE
)
```



#Question 5
## IgM as a predictor for IgG RBD and Spike

```{r}
#Extract all Baseline readings
Baseline<-Antibody_Data[Antibody_Data$`Sample type`=="Baseline",c(1,5,16,23,24,25,26,27,28,29,30,31,37,38,39,40,41,42,43,44,45,46,47,48)]

#Extract Acute and Convalescent Samples with Symptom onset between 16-40 Days
Acute_temp<-Antibody_Data[Antibody_Data$`Sample type`=="Acute" & Antibody_Data$`Days post First Symptom onset`>15 & Antibody_Data$`Days post First Symptom onset`<41 & Antibody_Data$`Days post Last vax`<0,c(1,5,16,23,24,25,26,27,28,29,30,31,37,38,39,40,41,42,43,44,45,46,47,48,8)]
Convalescent_temp<-Antibody_Data[Antibody_Data$`Sample type`=="Convalescent" & Antibody_Data$`Days post First Symptom onset`>15 & Antibody_Data$`Days post First Symptom onset`<41 ,c(1,5,16,23,24,25,26,27,28,29,30,31,37,38,39,40,41,42,43,44,45,46,47,48,8)]

Acute_temp<-Acute_temp[complete.cases(Acute_temp),]
Convalescent_temp<-Convalescent_temp[complete.cases(Convalescent_temp),]
Infectives<-rbind(Acute_temp,Convalescent_temp)

Merged<- merge(y=Infectives, x=Baseline, by="SJTRCID", all=TRUE,suffixes = c(".Baseline",".Infectives"));


```

Multiple Linear Regression for RBD_IgG
```{r}
linear_model_RBD<-lm(Finalset$RBD_IgG.Infectives ~ Finalset$OC43_IgM.Baseline + Finalset$HKU1_IgM.Baseline+Finalset$NL63_IgM.Baseline+Finalset$`229E_IgM.Baseline` + Finalset$`Days post First Symptom onset`, data = Finalset)
summary(linear_model_RBD)


```

Multiple Linear Regression for Spike_IgG
```{r}
linear_model_RBD<-lm(Finalset$Spike_IgG.Infectives ~ Finalset$OC43_IgM.Baseline + Finalset$HKU1_IgM.Baseline+Finalset$NL63_IgM.Baseline+Finalset$`229E_IgM.Baseline` + Finalset$`Days post First Symptom onset`, data = Finalset)
summary(linear_model_RBD)

```

Linear regression with best two predictors from previous model.
```{r}

linear_model_RBD<-lm(Finalset$Spike_IgG.Infectives ~ Finalset$`229E_IgM.Baseline` + Finalset$NL63_IgM.Baseline, data = Finalset)
summary(linear_model_RBD)
```

# Question 5
## Correlations between IgM CCOV sum at Baseline  Acute and Convalescent samples taken from 16-40 days post symptom onset


Extract indiviudals who have not recieved a vaccine based on last vaccine day column, and who have results reported between 16-40 days
```{r}

#Extract all Baseline readings
Baseline<-Antibody_Data[Antibody_Data$`Sample type`=="Baseline",col_list]

#Extract Acute and Convalescent Samples with Symptom onset between 16-40 Days
Acute_temp<-Antibody_Data[Antibody_Data$`Sample type`=="Acute" & Antibody_Data$`Days post First Symptom onset`>15 & Antibody_Data$`Days post First Symptom onset`<41& Antibody_Data$`Days post Last vax`<0,col_list]
Convalescent_temp<-Antibody_Data[Antibody_Data$`Sample type`=="Convalescent" & Antibody_Data$`Days post First Symptom onset`>15 & Antibody_Data$`Days post First Symptom onset`<41 ,col_list]

Acute_temp<-Acute_temp[complete.cases(Acute_temp),]
Convalescent_temp<-Convalescent_temp[complete.cases(Convalescent_temp),]
Infectives<-rbind(Acute_temp,Convalescent_temp)

Merged<- merge(y=Infectives, x=Baseline, by="SJTRCID", all=TRUE,suffixes = c(".Baseline",".Infectives"));

Finalset<-Merged[complete.cases(Merged),]

#Sum IgM
Finalset$`SumIgM`<-(Finalset[,17]+Finalset[,18]+Finalset[,19]+Finalset[,20])

```

```{r}
temp<-Finalset[,c(49,27,28,29,30,31,32,33,34,35)]

pairs.panels(temp, 
             method = "pearson", # correlation method
             hist.col = "#00AFBB",
             density = TRUE,  # show density plots
             ellipses = FALSE,  # show correlation ellipses
             cor = TRUE,
             stars = TRUE,
             cex.cor = 3,
             lm=TRUE)

```



# Question 6 
## Correlations between CCOV at Baseline and PV samples 


Extract indiviudals who have not recieved a vaccine based on last vaccine day column, and who have results reported between 16-40 days

##Boost between postvaccine and baseline

```{r}

#Extract all Baseline readings
Baseline<-Antibody_Data[Antibody_Data$`Sample type`=="Baseline" & Antibody_Data$`Confirmed COVID`==0,c(1,5,39,40,41,42,43,44,45,46,47,48,49,50)]

post_vaccine<-Vaccine_Data[Vaccine_Data$`Days post Last vax`<86 ,col_list]

Merged<- merge(y=post_vaccine, x=Baseline, by="SJTRCID", all=TRUE,suffixes = c(".Baseline",".PV"));

Finalset<-Merged[complete.cases(Merged),]
#Boost IgG
Finalset$OC34IgGBoost<-(Finalset[,25]-Finalset[,3])/Finalset[,3]
Finalset$NL63IgGBoost<-(Finalset[,26]-Finalset[,4])/Finalset[,4]
Finalset$`229EIgGBoost`<-(Finalset[,27]-Finalset[,5])/Finalset[,5]
Finalset$`HKU1IgGBoost`<-(Finalset[,28]-Finalset[,6])/Finalset[,6]

#Boost IgM
Finalset$`OC43IgMBoost`<-(Finalset[,29]-Finalset[,7])/Finalset[,7]
Finalset$NL63IgMBoost<-(Finalset[,30]-Finalset[,8])/Finalset[,8]
Finalset$`229EIgMBoost`<-(Finalset[,31]-Finalset[,9])/Finalset[,9]
Finalset$`HKU1IgMBoost`<-(Finalset[,32]-Finalset[,10])/Finalset[,10]

#Boost IgA
Finalset$`OC43IgABoost`<-(Finalset[,33]-Finalset[,11])/Finalset[,11]
Finalset$NL63IgABoost<-(Finalset[,34]-Finalset[,12])/Finalset[,12]
Finalset$`229EIgABoost`<-(Finalset[,35]-Finalset[,13])/Finalset[,13]
Finalset$`HKU1IgABoost`<-(Finalset[,36]-Finalset[,14])/Finalset[,14]
```

CCOV Baseline vs IgG Post vaccine response
```{r}

temp<-Finalset[,c(3,6,5,4,7,10,9,8,11,14,13,12,16,17,18)]

pairs.panels(temp, 
             method = "pearson", # correlation method
             hist.col = "#00AFBB",
             density = TRUE,  # show density plots
             ellipses = FALSE,  # show correlation ellipses
             cor = TRUE,
             stars = TRUE,
             cex.cor = 2,
             lm=TRUE)

ApplyFdrCor(
temp,
alpha = 0.05,
stat_test = "empirical",
method = "LCTnorm",
Nboot = 1000,
vect = FALSE,
arr.ind = FALSE
)
```

CCOV Baseline vs IgM Post vaccine response

```{r}
temp<-Finalset[,c(3,6,5,4,7,10,9,8,11,14,13,12,19,20,21)]

pairs.panels(temp, 
             method = "pearson", # correlation method
             hist.col = "#00AFBB",
             density = TRUE,  # show density plots
             ellipses = FALSE,  # show correlation ellipses
             cor = TRUE,
             stars = TRUE,
             cex.cor = 2,
             lm=TRUE)

ApplyFdrCor(
temp,
alpha = 0.05,
stat_test = "empirical",
method = "LCTnorm",
Nboot = 1000,
vect = FALSE,
arr.ind = FALSE
)
```

CCOV Baseline vs IgA Post vaccine response
```{r}
temp<-Finalset[,c(3,6,5,4,7,10,9,8,11,14,13,12,22,23,24)]

pairs.panels(temp, 
             method = "pearson", # correlation method
             hist.col = "#00AFBB",
             density = TRUE,  # show density plots
             ellipses = FALSE,  # show correlation ellipses
             cor = TRUE,
             stars = TRUE,
             cex.cor = 2,
             lm=TRUE)

ApplyFdrCor(
temp,
alpha = 0.05,
stat_test = "empirical",
method = "LCTnorm",
Nboot = 1000,
vect = FALSE,
arr.ind = FALSE
)

```

CCOV Boost vs IgG Post vaccine response
```{r}

temp<-Finalset[,c(37,40,39,38,41,44,43,42,45,48,47,46,16,17,18)]

pairs.panels(temp, 
             method = "pearson", # correlation method
             hist.col = "#00AFBB",
             density = TRUE,  # show density plots
             ellipses = FALSE,  # show correlation ellipses
             cor = TRUE,
             stars = TRUE,
             cex.cor = 3,
             lm=TRUE)

ApplyFdrCor(
temp,
alpha = 0.05,
stat_test = "empirical",
method = "LCTnorm",
Nboot = 1000,
vect = FALSE,
arr.ind = FALSE
)
```

CCOV Boost vs IgM Post vaccine response
```{r}

temp<-Finalset[,c(37,40,39,38,41,44,43,42,45,48,47,46,19,20,21)]

pairs.panels(temp, 
             method = "pearson", # correlation method
             hist.col = "#00AFBB",
             density = TRUE,  # show density plots
             ellipses = FALSE,  # show correlation ellipses
             cor = TRUE,
             stars = TRUE,
             cex.cor = 3,
             lm=TRUE)

ApplyFdrCor(
temp,
alpha = 0.05,
stat_test = "empirical",
method = "LCTnorm",
Nboot = 1000,
vect = FALSE,
arr.ind = FALSE
)
```
CCOV Boost vs IgA Post vaccine response
```{r}

temp<-Finalset[,c(37,40,39,38,41,44,43,42,45,48,47,46,22,23,24)]

pairs.panels(temp, 
             method = "pearson", # correlation method
             hist.col = "#00AFBB",
             density = TRUE,  # show density plots
             ellipses = FALSE,  # show correlation ellipses
             cor = TRUE,
             stars = TRUE,
             cex.cor = 3,
             lm=TRUE)

ApplyFdrCor(
temp,
alpha = 0.05,
stat_test = "empirical",
method = "LCTnorm",
Nboot = 1000,
vect = FALSE,
arr.ind = FALSE
)



```

